

```{r}
library(tidyverse)
library(haven)
library(here)
library(cowplot)
library(patchwork)
library(ggthemes)
library(MatchIt)
d <- read_sav(here("data/State Rice Farm Data.sav"))
```

# Helper functions 

```{r}
# Variable used to control for demographics in the paper
variables <- c("Female", "Age", "Hui", "FamilyIncomePerPerson", "MotherEducation")


# Function to generate all possible subsets 
generate_subsets <- function(variables) {
  subsets <- list() # Initialize an empty list to store subsets
  
  for (i in 0:length(variables)) {
    # Generate all combinations of length i
    comb <- combn(variables, i, simplify = FALSE)
    subsets <- c(subsets, comb) # Add the combinations to the list of subsets
  }
  
  return(subsets)
}


# Generate regression model formula from the specified variables
convert_subsets_to_formula <- function(all_subsets, measure){
  all_formula <- lapply(all_subsets, 
         function(vars){
           if (identical(vars, character(0))){
             results = paste0(measure, " ~ RiceFarm")
           }else{
             var_string = paste(vars, sep = "+", collapse = " + ")
             results = paste(measure, "~", var_string, "+ RiceFarm")
  
           }
           return (results)
         })
  return (all_formula)
}

all_subsets <- generate_subsets(variables)
```

# Set up models 

```{r}
all_sociogram_models <- convert_subsets_to_formula(all_subsets, "SelfInflationFamily")
all_strangers_models <- convert_subsets_to_formula(all_subsets, "FriendStrangerDistinction")
all_triad_models <- convert_subsets_to_formula(all_subsets, "y")
```


# Set up the corresponding propensity matching dataset 

```{r}
set_up_matching_dataset <- function(raw_data, variable, task){
  
  if(length(variable) == 0){
    
    return (raw_data)
 
  }else{
    
    if(task == "SelfInflationFamily"){
      with_task <- c(variable, "SelfInflationFamily")
      with_rice <- c(with_task, "RiceFarm")
    }else if(task == "FriendStrangerDistinction"){
      with_task <- c(variable, "FriendStrangerDistinction")
      with_rice <- c(with_task, "RiceFarm")
    }else if(task == "RelationalPairing"){
      with_task <- c(variable, "RelationalPairing")
      with_rice <- c(with_task, "RiceFarm")
    }
    
    new_d <- d[,with_rice]
    new_d <- new_d[apply(new_d, 1, function(row) all(ifelse(is.numeric(row), row < 10000, TRUE))), ] 
    new_d <- new_d %>% filter(across(everything(), ~ !is.na(.)))
  
  var_string = paste(variable, sep = "+", collapse = " + ")
  glm_spec = paste("RiceFarm", "~", var_string)
  Matching<-glm(as.formula(glm_spec), family = binomial(), data = new_d)

  PropensityScores <- data.frame(pr_score = predict(Matching, type = "response"),RiceFarm= Matching$model$RiceFarm)
  
  mod_match <- matchit(as.formula(glm_spec), method = "optimal", data = new_d) 
  
  matched_ds <- match.data(mod_match)
  return (matched_ds)

  
  }
}



all_SelfInflationFamily_matching_dataset <- lapply(all_subsets, function(vars){
  print(vars)
  set_up_matching_dataset(d, vars, "SelfInflationFamily")
})

all_FriendStrangerDistinction_matching_dataset <- lapply(all_subsets, function(vars){
  print(vars)
  set_up_matching_dataset(d, vars, "FriendStrangerDistinction")
})

all_RelationalPairing_matching_dataset <- lapply(all_subsets, function(vars){
  print(vars)
  set_up_matching_dataset(d, vars, "RelationalPairing")
})
```


# Set up propensity matching dataset as the original paper

Code from the below snippet is adapted from the OSF repository of the original paper.

```{r}
# sociogram matching dataset
triad <- d
triad <- data.frame(triad$RiceFarm, triad$FamilyIncomePerPerson, triad$Age, triad$Female, triad$MotherEducation, triad$SelfInflationFamily, triad$Hui)
colnames(triad)<-c("RiceFarm", "FamilyIncomePerPerson", "Age", "Female", "MotherEducation","SelfInflationFamily","Hui")
triad <-subset(triad, triad$RiceFarm<10000)
triad <-subset(triad, triad$FamilyIncomePerPerson<10000)
triad <-subset(triad, triad$Age<10000)
triad <-subset(triad, triad$Female<10000)
triad <-subset(triad, triad$MotherEducation<10000)
triad <-subset(triad, triad$SelfInflationFamily <10000)
triad <-subset(triad, triad$Hui<10000)
summary(Matching<-glm(RiceFarm ~ FamilyIncomePerPerson+Age+Female+MotherEducation, family = binomial(), data = triad))
PropensityScores <- data.frame(pr_score = predict(Matching, type = "response"),RiceFarm= Matching$model$RiceFarm)
head(PropensityScores)
# mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation, method = "optimal", data = triad)
mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation+Hui, method = "optimal", data = triad)
sociogram_match_ds <- match.data(mod_match)

# friends stranger matching dataset
triad <-d
triad <- data.frame(triad$RiceFarm, triad$FamilyIncomePerPerson, triad$Age, triad$Female, triad$MotherEducation, triad$FriendStrangerDistinction, triad$Hui, triad$RewardHonestFriend,triad$RewardHonestStranger,triad$PunishDishonestFriend,triad$PunishDishonestStranger)
colnames(triad)<-c("RiceFarm", "FamilyIncomePerPerson", "Age", "Female", "MotherEducation","FriendStrangerDistinction","Hui","RewardHonestFriend","RewardHonestStranger","PunishDishonestFriend","PunishDishonestStranger")
triad <-subset(triad, triad$RiceFarm<10000)
triad <-subset(triad, triad$FamilyIncomePerPerson<10000)
triad <-subset(triad, triad$Age<10000)
triad <-subset(triad, triad$Female<10000)
triad <-subset(triad, triad$MotherEducation<10000)
triad <-subset(triad, triad$FriendStrangerDistinction <10000)
triad <-subset(triad, triad$Hui<10000)
#Matching on the variables below.
summary(Matching<-glm(RiceFarm ~ FamilyIncomePerPerson+Age+Female+MotherEducation, family = binomial(), data = triad))
PropensityScores <- data.frame(pr_score = predict(Matching, type = "response"),RiceFarm= Matching$model$RiceFarm)
# mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation, method = "optimal", data = triad)
mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation+Hui, method = "optimal", data = triad)
stranger_matche_ds <- match.data(mod_match)

# holistic thoughts dataset
triad <- d
triad <- data.frame(triad$RiceFarm, triad$FamilyIncomePerPerson, triad$Age, triad$Female, triad$MotherEducation, triad$RelationalPairing, triad$Hui)
colnames(triad)<-c("RiceFarm", "FamilyIncomePerPerson", "Age", "Female", "MotherEducation","RelationalPairing","Hui")
triad <-subset(triad, triad$RiceFarm<10000)
triad <-subset(triad, triad$FamilyIncomePerPerson<10000)
triad <-subset(triad, triad$Age<10000)
triad <-subset(triad, triad$Female<10000)
triad <-subset(triad, triad$MotherEducation<10000)
triad <-subset(triad, triad$RelationalPairing<10000)
triad <-subset(triad, triad$Hui<10000)
summary(Matching<-glm(RiceFarm ~ FamilyIncomePerPerson+Age+Female+MotherEducation, family = binomial(), data = triad))
PropensityScores <- data.frame(pr_score = predict(Matching, type = "response"),RiceFarm= Matching$model$RiceFarm)
head(PropensityScores)
# mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation, method = "optimal", data = triad)
mod_match <- matchit(RiceFarm~ FamilyIncomePerPerson+Age+Female+MotherEducation+Hui, method = "optimal", data = triad)
summary(mod_match)
holistic_match_ds <- match.data(mod_match)
numY <- holistic_match_ds$RelationalPairing
numN <- with(holistic_match_ds, 14 - numY)
y <- cbind(numY, numN)
```

# Run model on the fully propensity matched dataset

```{r}

sociogram_fully_matched_res <- lapply(seq(1, length(all_sociogram_models)), 
       function(id){
         m = all_sociogram_models[[id]]
         data = all_SelfInflationFamily_matching_dataset[[id]]
         model = lm(as.formula(m), data = data)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()


stranger_fully_matched_res <- lapply(seq(1, length(all_strangers_models)), 
       function(id){
         m = all_strangers_models[[id]]
         data = all_FriendStrangerDistinction_matching_dataset[[id]]
         model = lm(as.formula(m), data = data)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()

holistic_fully_matched_res <- lapply(seq(1, length(all_RelationalPairing_matching_dataset)), 
       function(id){
         print(id)
         m = all_triad_models[[id]]
         data = all_RelationalPairing_matching_dataset[[id]]
         
         numY <- data$RelationalPairing
         numN <- with(data, 14 - numY)
         y <- cbind(numY, numN)
         
         model = glm(as.formula(m), data = data, binomial)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()

```


# Run model on the original propensity matching dataset 

```{r}
sociogram_matched_res <- lapply(all_sociogram_models, 
       function(m){
         model = lm(as.formula(m), data = sociogram_match_ds)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()

stranger_matched_res <- lapply(all_strangers_models, 
       function(m){
         model = lm(as.formula(m), data = stranger_matche_ds)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()


holistic_matched_res <- lapply(all_triad_models, 
       function(m){
         model = glm(as.formula(m), data = holistic_match_ds, binomial)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()
```

# Run model on the unmatched dataset

```{r}
sociogram_nonmatched_res <- lapply(all_sociogram_models, 
       function(m){
         model = lm(as.formula(m), data = d)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()

stranger_nonmatched_res <- lapply(all_strangers_models, 
       function(m){
         model = lm(as.formula(m), data = d)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()

numY <- d$RelationalPairing
numN <- with(d, 14 - numY)
y <- cbind(numY, numN)

holistic_nonmatched_res <- lapply(all_triad_models, 
       function(m){
         model = glm(as.formula(m), data = d, binomial)
         res = broom::tidy(model, conf.int	= TRUE) %>% mutate(model = m)
       }) %>% 
  bind_rows()
```

# Processing dataframe for visualization

```{r}
sociogram_res <- bind_rows(
        sociogram_fully_matched_res %>% mutate(type = "Model Matched"),
        sociogram_matched_res %>% mutate(type = "Original Matched"), 
          sociogram_nonmatched_res %>% mutate(type = "Non-matched")) %>% 
  filter(term == "RiceFarm") %>% 
  group_by(type) %>% 
  mutate(model_id = paste0("Model",row_number())) %>% 
  mutate(model_id = case_when(
    model == "SelfInflationFamily ~ RiceFarm" ~ "Rice/Wheat Only", 
    model == "SelfInflationFamily ~ Female + Age + Hui + FamilyIncomePerPerson + MotherEducation + RiceFarm" ~ "Reported Model", 
    TRUE ~ as.character(model_id)
  )) %>% 
  mutate(Significant = p.value < 0.05) %>% 
  mutate(Significant = if_else(Significant, "p < 0.05", "N.S."))
  
stranger_res <- bind_rows(
          stranger_fully_matched_res %>% mutate(type = "Model Matched"),
          stranger_matched_res %>% mutate(type = "Original Matched"), 
          stranger_nonmatched_res %>% mutate(type = "Non-matched")) %>% 
  filter(term == "RiceFarm") %>% 
  group_by(type) %>% 
  mutate(model_id = paste0("Model",row_number())) %>% 
  mutate(model_id = case_when(
    model == "FriendStrangerDistinction ~ RiceFarm" ~ "Rice/Wheat Only", 
    model == "FriendStrangerDistinction ~ Female + Age + Hui + FamilyIncomePerPerson + MotherEducation + RiceFarm" ~ "Reported Model", 
    TRUE ~ as.character(model_id)
  )) %>% 
  mutate(Significant = p.value < 0.05) %>% 
  mutate(Significant = if_else(Significant, "p < 0.05", "N.S."))

holistic_res <- bind_rows(
          holistic_fully_matched_res %>% mutate(type = "Model Matched"),
          holistic_matched_res %>% mutate(type = "Original Matched"), 
          holistic_nonmatched_res %>% mutate(type = "Non-matched")) %>% 
  filter(term == "RiceFarm") %>% 
  group_by(type) %>% 
  mutate(model_id = paste0("Model",row_number())) %>% 
  mutate(model_id = case_when(
    model == "y ~ RiceFarm" ~ "Rice/Wheat Only", 
    model == "y ~ Female + Age + Hui + FamilyIncomePerPerson + MotherEducation + RiceFarm" ~ "Reported Model", 
    TRUE ~ as.character(model_id)
  )) %>% 
  mutate(Significant = p.value < 0.05) %>% 
  mutate(Significant = if_else(Significant, "p < 0.05", "N.S."))

```

lib# Visualization

## Sociogram

```{r}

sociogram_res$type = factor(sociogram_res$type, levels = c("Non-matched", 
                                                           "Original Matched", 
                                                           "Model Matched"))
  
sociogram_plot <- sociogram_res %>% 
  ggplot(aes(model = estimate, x= reorder_within(model_id, estimate, type), y = estimate, ymin = conf.low, ymax = conf.high, color = Significant)) + 
  geom_pointrange() + 
  scale_x_reordered() +
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  scale_color_manual(values = c( "red", "black"))+
  coord_flip() +
  theme_few() + 
  xlab("") + 
  ylab("Estimate on Rice/Wheat") + 
  labs(title = "Self-Inflation (Family)")  + 
  facet_wrap(~type, scales = "free_y") + 
   theme(legend.position = "None", 
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.title=element_text(size=8), 
        axis.text.y = element_text(size = 6))

sociogram_plot

```

## Loyalty/Nepotism

```{r}

stranger_res$type = factor(stranger_res$type, levels = c("Non-matched", 
                                                           "Original Matched", 
                                                           "Model Matched"))
stranger_plot <- stranger_res %>% 
  ggplot(aes(model = estimate, x= reorder_within(model_id, estimate, type), y = estimate, ymin = conf.low, ymax = conf.high, color = Significant)) + 
    scale_x_reordered() +

  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  scale_color_manual(values = c(  "black","red"))+
  coord_flip() +
  theme_few() + 
  xlab("") + 
  ylab("Estimate on Rice/Wheat") + 
  labs(title = "Loyalty/Nepotism")  + 
  facet_wrap(~type, scales = "free_y") +
  theme(legend.position = "None")+ 
  theme(legend.position = "None", 
        plot.title = element_text(hjust = 0.5, size = 10),
        axis.title=element_text(size=8), 
        axis.text.y = element_text(size = 6))

stranger_plot
```

## Triads 

```{r}


holistic_res$type = factor(holistic_res$type, levels = c("Non-matched", 
                                                           "Original Matched", 
                                                           "Model Matched"))

rc_plot <- holistic_res %>% 
  ggplot(aes(model = estimate, x= reorder_within(model_id, estimate, type), y = estimate, ymin = conf.low, ymax = conf.high, color = Significant)) + 
  scale_x_reordered() +
  geom_pointrange() + 
  geom_hline(yintercept = 0, color = "gray", linetype = "dashed") + 
  scale_color_manual(values = c(  "black","red"))+
  coord_flip() +
  theme_few() + 
  xlab("") + 
  guides(color = guide_legend(title = "")) + 
  labs(title = "Relational Categorizations")  + 
  ylab("Estimate on Rice/Wheat") + 
  facet_wrap(~type, scales = "free_y") +
    theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5, size = 10), 
        axis.title=element_text(size=8),
        axis.text.y = element_text(size = 6))

rc_plot
```

## Everything together 

```{r fig.width=8, fig.height=12}
all_plots <- plot_grid(sociogram_plot,stranger_plot,rc_plot, nrow = 3, rel_heights = c(1.5, 1.5, 1.7))

all_plots

saveRDS(all_plots, here("cached_data/ma_plot.Rds"))
```


